Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-09-11 Ben_Manuscripts/structure_paper/Draft.tex
new analysis of disorder in quenched systems

  We parameterized the liquid crystal monomer Na-GA3C11 using the Generalized AMBER
  Force Field (GAFF) \cite{wang_development_2004} with the Antechamber package
  \cite{wang_automatic_2006} provided with AmberTools16
  \cite{case_ambertools16_2016}. We assigned atomic charges using the am1bccsym
  method of \texttt{molcharge} shipped with QUACPAC from Openeye Scientific
  Software. We ran all molecular dynamics simulations using GROMACS 2016
  \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.

@@

  To calculate the equilibrated pore spacing, we measured the distance between
  pore centers. We located the pore centers by averaging the coordinates of sodium
  ions in their respective pores. We generated pore spacing statistics 
  using the bootstrapping technique (See section S-\ref{S-section:p2p_stats} of the
  Supporting Information).

@@

  We can explain the discrepancies between R-$\pi$ seen experimentally
  and in simulation using what we have shown in this section. The stacking
  distance between monomer head groups is too large, likely due to failures
  of the forcefield to appropriately model $\pi-\pi$ interactions. The intensity
  of the simulated R-$\pi$ is too high, which may be a consequence of too much short-range
  ordering in the $z$-direction in addition to high degrees of correlation 
  between columns. Finally, the $q_r$ cross-section of R-$\pi$ is not smooth, 
  which is also likely a consequence of columns that are too highly correlated.

  The architecture of each column is therefore likely in between sandwiched and parallel
  displaced. The parallel displaced configuration that we have simulated in this
  paper is an exaggerated manifestation of the parallel displaced $\pi-\pi$
  stacking mode. The experimental WAXS pattern shows faint off-axis features at the
  same $q_r$ value as R-double which is only present in simulated patterns generated from
  parallel displaced configurations. The monomers may prefer to be parallel displaced, but
  their displacement is likely only slightly shifted, on the $xy$ plane, from the
  center of mass of their vertically adjacent neighbors. In this way, columns can
  more easily act independently while maintaining a parallel displaced structure.

  Because disorder among head groups in the simulated atomistic systems is largely
  determined by each system's quenched configuration, one would need to average an
  ensemble of simulations in order to optimally match the experimental WAXS pattern. 
  Both the initial configuration and initial velocity randomization lead to 
  different quenched configurations every time we run an equilibration simulation.
  Although the simulated XRD pattern changes dynamically as we simulate the system
  due to thermal fluctuations, its features are largely determined by the initial 
  quenched configuration. Here we assume that the timescales for large scale 
  rearrangements of the system are much longer than what we can feasibly simulate. 
  %MRS12: I don't think this is necessary.  They should reproduce the same findings, if they use a similar quenched configuration. 
  %As a result, it will be difficult to exactly reproduce the work here, but we are
  %confident that one can draw the same conclusions using our methodology.

@@

  We calculated the ionic conductivity of the parallel displaced configuration in
  the ordered basin with 1 wt\% water since we believe its structure is the 
  closest match to experiment. Our model estimates the ionic conductivity within
  one order of magnitude of experiment (Figure~\ref{fig:ionic_conductivity}). We
  verified the value calculated by the Nernst-Einstein relationship using 
  the collective diffusion model\cite{liu_collective_2013} 
  (See section S~\ref{S-fig:conductivity}). The values calculated by the 
  collective diffusion model agree with Nernst-Einstein  values within error, 
  however there is a much higher uncertainty that would require much longer 
  simulations to lower.

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{IC_nernst.png}
  \caption{The calculated ionic conductivity of the simulated system is approximately
  one order of magnitude higher than experiment.}\label{fig:ionic_conductivity}
  \end{figure}

@@

  We achieve maximum structural consistency with experiment, as determined by
  simulated 2D XRD patterns, when we build our model in the ordered basin
  parallel displaced configuration with 5 monomer columns per pore and 1 wt\%
  water. R-alkanes and R-pores appear where expected for the reasons originally
  predicted. We find that R-spots is likely due to ordered alkane chain packing.
  R-$\pi$ appears at lower q values than experiment because monomer stack too far
  apart, and its intensity is far too high, likely because our initial
  configurations contain a high level of dependence between monomer columns.
  Finally, we observed that our model can only produce R-double when we add small amounts of
  % I removed the specific details, since it implied that 2% wouldn't do it, which we don't know.
  %1 wt\% 
water to the system. This observation has possible implications for the
  reproducibility of the experimental results from Feng et al. since they claim
  that their membrane is completely dry.

@@

>>>>

  We parameterized the interaction potential for the liquid crystal monomer 
  Na-GA3C11 using the Generalized AMBER Force Field (GAFF) 
  \cite{wang_development_2004} with the Antechamber package \cite{wang_automatic_2006} 
  provided with AmberTools16 \cite{case_ambertools16_2016}. We assigned atomic
  charges using the am1bccsym method of \texttt{molcharge} shipped with QUACPAC
  from Openeye Scientific Software. We ran all molecular dynamics simulations 
  using GROMACS 2016 \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.

@@

  To calculate the equilibrated pore spacing, we measured the distance between
  pore centers. We located the pore centers by averaging the coordinates of sodium
  ions in their respective pores. We generated pore spacing statistics 
  using the bootstrapping technique (See section S-\ref{S-section:p2p_stats} of the
  Supporting Information). 
  % BJC15: added to address Matt's concern
  The pore spacings calculated in this way are consistent
  with one half of the $x$ and $y$ box vectors (See, Table S-\ref{S-table:p2p}). However
  our method for their calculation does a better job capturing the spread of 
  pore-to-pore distances.

@@

  We can explain the discrepancies between R-$\pi$ seen experimentally
  and in simulation using what we have shown in this section. The stacking
  distance between monomer head groups is too large, likely due to failures
  of the force field to appropriately model $\pi-\pi$ interactions. The intensity
  of the simulated R-$\pi$ is too high, which may be a consequence of too much short-range
  ordering in the $z$-direction in addition to high degrees of correlation 
  between columns. Finally, the $q_r$ cross-section of R-$\pi$ is not smooth, 
  which is also likely a consequence of columns that are too highly correlated.

  % BJC15 : Matt comment: "I found the discussion of pore structure in the first 
  % full paragraph on page 38 is a bit hard to follow. Maybe a schematic of what 
  % “in between sandwiched and parallel displaced” looks like would be helpful"
  The architecture of each column is therefore likely in between our sandwiched and parallel
  displaced configurations. The parallel displaced configuration that we have simulated in this
  paper is an exaggerated manifestation of the parallel displaced $\pi-\pi$
  stacking mode. The experimental WAXS pattern shows faint off-axis features at the
  same $q_r$ value as R-double which is only present in simulated patterns generated from
  parallel displaced configurations. The monomers may prefer to be parallel displaced, but
  their displacement is likely only slightly shifted, on the $xy$ plane, from the
  center of mass of their vertically adjacent neighbors. In this way, columns can
  more easily act independently while maintaining a parallel displaced structure.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{pd_36.eps}
  \caption{}\label{fig:pd_36}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{pd_lt36.eps}
  \caption{}\label{fig:pd_lt36}
  \end{subfigure}
  \caption{Head groups are likely stack in a configuration between sandwiched and
  parallel displaced. (a) In our parallel displaced configurations with 5 monomers 
  per columns, we placed head groups so the angle, $\theta$, between vectors extending
  from vertically stacked head groups to the pore center equals 36$\degree$ 
  ((360$\degree$ / $ncol$) / 2 where $ncol$ is the number of columns per pore). 
  (b) In the true configuration, $\theta$ is likely between 0$\degree$ and 36 $\degree$.
  When $\theta$=0$\degree$, the system architecture is the same as a sandwiched 
  configuration.}\label{fig:between_pd}
  \end{figure}

% BJC15: this paragraph reframed and expanded below
%  Because disorder among head groups in the simulated 
%  atomistic systems is largely determined by each system's quenched configuration,
%  one would need to average an ensemble of simulations in order to optimally match the experimental WAXS pattern. 
%  Both the initial configuration and initial velocity randomization lead to 
%  different quenched configurations every time we run an equilibration simulation.
%  Although the simulated XRD pattern changes dynamically as we simulate the system
%  due to thermal fluctuations, its features are largely determined by the initial 
%  quenched configuration. Here we assume that the timescales for large scale 
%  rearrangements of the system are much longer than what we can feasibly simulate.

  Since the dynamics of this system appear to be quite slow, we can learn more about
  their time-averaged structure by studying ensembles of simulations.
  Disorder among head groups in the simulated atomistic systems is largely determined
  by each system's quenched configuration. We observe rapid reorganization of our 
  initial configurations into configurations with quenched disorder that does not
  vary significantly for the remainder of the % BJC15: I could quantify this more and put in supporting info
  simulation time. For that reason, we created ensembles of 40 simulations in both
  the parallel displaced and sandwiched configurations. We used the same equilibration
  technique as above (see section~\ref{section:equilibration}), however we stopped 
  the equilibration after 5 ns of unrestrained simulation. We simulated XRD patterns
  from the 40 concatenated trajectories. The $q_r$ cross-sections generated from the 
  two concatenated trajectories are shown in Figure~\ref{fig:ensemble_XRD}. 
  Qualitatively, the $q_r$ cross-sections of R-$\pi$ are nearly smooth, with small
  spikes near $q_r$=0. The data suggests that the average
  intensity of R-$\pi$ in sandwiched systems is about 3$\times$ higher than that in the
  parallel displaced configuration. Overall, the intensity of R-$\pi$ generated from the
  parallel displaced ensemble shows the best agreement with experiment so far. For
  simplicity, we will limit the following discussion to the parallel displaced 
  configuration. Equivalent data is available for the sandwiched configuration in the
  supporting information.
  %BJC15: limiting discussion to parallel displaced since it seems most consistent with experiment
  % However, I can switch it sandwiched very easily.

  %BJC15: This figure might not be necessary. Do the comparisons of emperical
  % cumulative distribution functions make the same point? 
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ensemble_rsection.png}
  \caption{Sandwiched}\label{fig:sandwiched_ensemble_rsection}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_rsection.png}
  \caption{Parallel Displaced}\label{fig:offset_ensemble_rsection}
  \end{subfigure}
  \caption{The $q_r$ section of R-$\pi$ is much smoother when simulated XRD patterns
  		   are generated from an ensemble of 40 independent simulations. The maximum 
  		   intensity of R-$\pi$ is 3$\times$ higher in the sandwiched configuration (a)
  		   than in the parallel displaced configuration (b).}\label{fig:ensemble_XRD}
  \end{figure}

  Independent simulations exhibit similar amounts of quenched disorder. For 
  each, we measured the deviation of the head group centers of mass from their
  idealized positions (see section~\ref{method:simple_systems}). 
  We created histograms of the standard deviations of each distribution which
  are shown in Figure~\ref{fig:ensemble_stds}. The distributions of standard deviations
  are fairly tight with ($\sigma_\sigma_z$, $\sigma_\sigma_r$, $\sigma_\sigma_\theta$) = (0.011 nm, 
  0.007 nm , 0.022 radians). We pooled the deviations from idealized positions 
  from all independent simulations in order to create the distributions shown in 
  Figure~\ref{fig:offset_ensemble_pooled}. The distributions appear 
  symmetric meaning that there is an equal chance for a head group to displace
  in the positive or negative $z$, $r$ or $\theta$-direction. We verified that
  this is the case for individual center of masses. 
  % For a given system, there are 400 head groups. 
  If we consider the center of mass of the first head group, we expect that the
  distribution of its deviation from its idealized position among all the 
  independent simulations
%  the $z$, $r$, and $\theta$ directions 
  should be symmetric about its idealized position. We can calculate the 
  empirical cumulative distribution function (ECDF) 
  of this distribution of deviations. 
  % Each ECDF contains 40 data points, one from each independent simulation.
  The ECDFs of 5 randomly selected centers of 
  mass are shown in Figure~\ref{fig:offset_ecdfs} (colored lines). We also calculated 
  the ECDF from the full distributions in Figure~\ref{fig:offset_ensemble_pooled}
  (black line with error bars). We generated error bars that represent the 95\% 
  confidence intervals, by randomly sampling 40 values (the same as the number 
  of independent simulations) from the distributions in 
  Figure~\ref{fig:offset_ensemble_pooled}, then measuring the deviation between
  the sampled ECDF and the full ECDF. The center of mass ECDFs lie between the
  error bars of the full ECDF within reason. This provides further evidence that
  each center of mass moves independently, in random directions when systems
  quench.

% Sandwiched: (0.019 nm, 0.007 nm, 0.023 radians)

  \begin{figure}[!htb]
  \centering
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{sandwiched_ensemble_stds.png}
%  \caption{Sandwiched}\label{fig:sandwiched_ensemble_stds.png}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=0.45\textwidth]{offset_ensemble_stds.png}
%  \caption{Parallel Displaced}\label{fig:offset_ensemble_stds.png}
%  \end{subfigure}
  \caption{There is a narrow spread in the standard deviation of
  quenched disorder for each independent configuration.}\label{fig:ensemble_stds}
  \end{figure}

  %BJC15: will not waste much time formatting until we converge on a figure 
  \begin{figure}[!htb]
  \centering
%  \begin{subfigure}{\textwidth}
%  \includegraphics[width=\textwidth]{sandwiched_ensemble_pooled.png}
%  \caption{Sandwiched}\label{fig:sandwiched_ensemble_pooled.png}
%  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_pooled.png}
  \caption{Distributions of deviations from ideal positions generated with data
  from all independent simulations}\label{fig:offset_ensemble_pooled}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ecdfs.png}
  \caption{Emperical cumulative distribution functions generated from (a) and
  from simulation ensembles.}\label{fig:offset_ecdfs}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_regional_density.png}
  \caption{Radial density of select monomer components.}\label{fig:offset_ensemble_regional_density}
  \end{subfigure}
  \caption{The distributions of the deviations of head group center of masses
  from their idealized positions generated using pooled data from all
  frames of each independent configuration is symmetric. This implies that 
  there is equal probability for a head group to displace in the positive
  or negative $z$, $r$ or $\theta$-direction.}\label{fig:full_ensemble_distributions}
  \end{figure}

@@

  We calculated the ionic conductivity of the parallel displaced configuration in
  the ordered basin with 1 wt\% water since we believe its structure is the 
  closest match to experiment. Our model estimates the ionic conductivity to be
  $(5.92 \pm 0.05)\times$\num{e-5}~S/m, about 5 times higher than the experimental value of 
  $(1.3 \pm 0.1)\times$\num{e-5}~S/m. We verified the value calculated by the Nernst-Einstein
  relationship using the collective diffusion model\cite{liu_collective_2013} 
  (See section S~\ref{S-fig:conductivity}). The values calculated by the 
  collective diffusion model agree with Nernst-Einstein values within error, 
  however there is a much higher uncertainty that would require much longer 
  simulations to lower.

@@

% BJC15: removed figure
%  \begin{figure}
%  \centering
%  \includegraphics[width=0.5\textwidth]{IC_nernst.png}
%  \caption{The calculated ionic conductivity of the simulated system is approximately
%  one order of magnitude higher than experiment.}\label{fig:ionic_conductivity}
%  \end{figure}

@@

  We achieve maximum structural consistency with experiment, as determined by
  simulated 2D XRD patterns, when we build our model in the ordered basin
  parallel displaced configuration with 5 monomer columns per pore and 1 wt\%
  water. R-alkanes and R-pores appear where expected for the reasons originally
  predicted. We find that R-spots is likely due to ordered alkane chain packing.
  R-$\pi$ appears at lower q values than experiment because monomer stack too far
  apart, and its intensity is far too high, likely because our initial
  configurations contain a high level of dependence between monomer columns.
  Finally, we observed that our model can only produce R-double when we add 
  small amounts of water to the system. This observation has possible implications
  for the reproducibility of the experimental results from Feng et al. since they
  claim that their membrane is completely dry.

@@

  % BJC15: first pass at a brief future work paragraph
  Future work, based on what has been learned in this study, may help further improve the 
  structural agreement between experiment and simulation. We may be able to 
  modify the GAFF force field or use a different force field in order to better
  capture the $\pi-\pi$ interactions which draw stacked monomers closer together. 
  We can study ensembles of long simulations in order to observe more averaged 
  structure and to create more experimentally consistent XRD patterns. Finally, we can
  run extremely long simulations (on the order of \SI{}{\micro s}) in order to better 
  quantify the time scales for large scale rearrangements to occur.

### 2018-09-11 Ben_Manuscripts/structure_paper/supporting_information.tex
new analysis of disorder in quenched systems

%  \section{Calculation of pore-to-pore spacing statistics}\label{section:p2p_stats}
% 
% %BJC: is it really necessary to explain this if I release the code? I don't explain
% %any of the other stats I calculate. 
%  We are interested in 5 pore-to-pore distances which should all be
%  equal in a perfect hexagonal array (Figure~\ref{fig:p2p_diagram}). Only 4 of
%  the 5 distances are independent. We can calculate a trajectory of spacing
%  versus time for each of the 5 distances. We calculated the average pore-to-pore
%  spacing and its uncertainty according to the following procedure:
%   \begin{enumerate}
%	\item We calculated the time when each of the pore-to-pore distances
%	were equilibrated using \\ \texttt{pymbar.timeseries.detectEquilibration()}
%	\cite{chodera_simple_2016,shirts_statistically_2008}. We began calculations
%	after the largest of the five values.
%	\item We calculated how long it takes for the data in each of the 5
%	trajectories to become uncorrelated using \texttt{pymbar.timeseries.integratedAutocorrelationTime()}
%	\cite{chodera_simple_2016,shirts_statistically_2008}. 
%	\item We broke the full equilibrated trajectory into blocks of length $\tau$, where
%	$\tau$ is the maximum of the five autocorrelation times calculated. Each block contains
%	five sub-trajectories of pore-to-pore spacings.   
%	\item We generate statistics using the bootstrapping technique. For
%	each bootstrap trial, we reconstruct an equilibrium trajectory by randomly
%	sampling from the trajectory blocks. 
%	\item The average pore-to-pore distance is the mean of all pore
%	spacings among all bootstrap trials.
%	\item To calculate the uncertainty in pore-to-pore distance, we calculate the average 
%	pore spacing for each pore over all bootstrap trials. Using the 5 average 
%	pore-to-pore distances, we calculate the spread with:
%	\begin{equation}
%	s = \sqrt{\frac{1}{4} \sum_{i=1}^5 (x_i - \overline{x})^2} 
%	\label{equation:p2p_stats}
%	\end{equation}
%	where $\overline{x}$ is the average pore-to-pore distance. We divided the sum in 
%	equation~\ref{equation:p2p_stats} by 4 since there are only 4 independent pore
%	spacings.
%	
%  \end{enumerate}
%  \begin{figure}[!htb]
%	\centering
%	\includegraphics[width=0.25\textwidth]{p2p_diagram.png}
%	\caption{There are five pore-to-pore distances that are equal in a perfect
%		hexagon. If each number in the diagram represents the center of a
%		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
%		4 to 3, 3 to 1 and 1 to 4 should be equal. Only 4 of the distances
%		are independent. For example, the distance from 1 to 4 is defined by
%		the location of all other pore centers.}
%	\label{fig:p2p_diagram}
%  \end{figure}

>>>>

  \section{Calculation of pore-to-pore spacing statistics}\label{section:p2p_stats}

 %BJC: is it really necessary to explain this if I release the code? I don't explain
 %any of the other stats I calculate. 
  We are interested in 5 pore-to-pore distances which should all be
  equal in a perfect hexagonal array (Figure~\ref{fig:p2p_diagram}). Only 4 of
  the 5 distances are independent. We can calculate a trajectory of spacing
  versus time for each of the 5 distances. We calculated the average pore-to-pore
  spacing and its uncertainty according to the following procedure:
   \begin{enumerate}
	\item We calculated the time when each of the pore-to-pore distances
	were equilibrated using \\ \texttt{pymbar.timeseries.detectEquilibration()}
	\cite{chodera_simple_2016,shirts_statistically_2008}. We began calculations
	after the largest of the five values.
	\item We calculated how long it takes for the data in each of the 5
	trajectories to become uncorrelated using \texttt{pymbar.timeseries.integratedAutocorrelationTime()}
	\cite{chodera_simple_2016,shirts_statistically_2008}. 
	\item We broke the full equilibrated trajectory into blocks of length $\tau$, where
	$\tau$ is the maximum of the five autocorrelation times calculated. Each block contains
	five sub-trajectories of pore-to-pore spacings.   
	\item We generate statistics using the bootstrapping technique. For
	each bootstrap trial, we reconstruct an equilibrium trajectory by randomly
	sampling from the trajectory blocks. 
	\item The average pore-to-pore distance is the mean of all pore
	spacings among all bootstrap trials.
	\item To calculate the uncertainty in pore-to-pore distance, we calculate the average 
	pore spacing for each pore over all bootstrap trials. Using the 5 average 
	pore-to-pore distances, we calculate the spread with:
	\begin{equation}
	s = \sqrt{\frac{1}{4} \sum_{i=1}^5 (x_i - \overline{x})^2} 
	\label{equation:p2p_stats}
	\end{equation}
	where $\overline{x}$ is the average pore-to-pore distance. We divided the sum in 
	equation~\ref{equation:p2p_stats} by 4 since there are only 4 independent pore
	spacings.

  \end{enumerate}
  \begin{figure}[!htb]
	\centering
	\includegraphics[width=0.25\textwidth]{p2p_diagram.png}
	\caption{There are five pore-to-pore distances that are equal in a perfect
		hexagon. If each number in the diagram represents the center of a
		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
		4 to 3, 3 to 1 and 1 to 4 should be equal. Only 4 of the distances
		are independent. For example, the distance from 1 to 4 is defined by
		the location of all other pore centers.}
	\label{fig:p2p_diagram}
  \end{figure}

  Alternatively, one can calculate the pore spacing as half of the $x$ and $y$
  box vectors, however this technique does not fully capture the uncertainty
  in the pore-to-pore distances.

  \begin{table}[h]
  \centering
  \begin{tabular}{cc}
  \toprule
  System                         & Pore Spacing ($nm$) & Pore Spacing ($nm$)              \\
                                 & Pore centers        & $\dfrac{x-box vector}{2}$ ($nm$) \\ 
  \midrule
  Sandwiched, Ordered            & 4.18 $\pm$ 0.13     & 4.16 $\pm$ 0.01                  \\
  Parallel Displaced, Ordered    & 4.17 $\pm$ 0.12     & 4.18 $\pm$ 0.01                  \\
  Sandwiched, Disordered         & 4.05 $\pm$ 0.14     & 4.01 $\pm$ 0.01                  \\
  Parallel Displaced, Disordered & 4.03 $\pm$ 0.07     & 4.01 $\pm$ 0.01                  \\
  \bottomrule
  \end{tabular}
  \caption{The pore spacing measured in two ways agree within uncertainty. In the main
  text, we report values calculated by measuring the average distance between pore centers. 
  Alternatively, one can estimate the pore spacing as half of the $x$ and $y$ box vectors.
  Both methods agree within uncertainty, but measuring the distance between pore centers
  does a better job of showing the spread of pore-to-pore distances.}~\label{table:p2p}
  \end{table}
